validateE2data

### 2018-08-17 E2/analysis/inspectHists.Rmd
about to build renaming columns into import

BJ has essentially zero efficacy and may have tended to report letters from beginning of stream in one condition.

SsWhoLookWeird<-c("CY","AP","BJ")

We'll see whether the statistical comparison of mixture modeling to guessing distribution flags these as not being fit significantly better by mixture model.

>>>>

BJ has essentially zero efficacy and may have tended to report letters from beginning of stream in one condition.
```{r }
SsWhoLookWeird<-c("CY","AP","BJ")
```
We'll see whether the statistical comparison of mixture modeling to guessing distribution flags these as not being fit significantly better by mixture model.

### 2018-08-17 E2/analysis/mixModelE2data.Rmd
about to build renaming columns into import

NaNs for targetSP indicate one-target trials, which are also indicated by targetSide==0
```{r}

table(E2$targetSP, E2$targetSide, dnn=c("targetSP","targetSide"), useNA="ifany")

```
Proportion of one-target trials seems to be 
`nrow(E2 %>% filter(targetSide!="Both")) / nrow(E2)`

@@

Fit mixture model (if fitting not previously done and cached). 
```{r, echo=FALSE}

library(mixRSVP)

@@

estimates<- df  %>%  filter( !is.nan(targetSP) ) %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

@@

Save the param estimates to a file.
```{Save param estimates, echo=FALSE}

write.csv(estimates, file = "Results/backwards2E2_paramEstimates.csv")
#saveRDS(estimates, file = "Data/backwards2E1_paramEstimates.rda", compress="bzip2")

>>>>

NaNs for targetSP indicate one-target trials, which are also indicated by targetSide==0
```{r}
table(E2$targetSP, E2$targetSide, dnn=c("targetSP","targetSide"), useNA="ifany")
```
Proportion of one-target trials seems to be 
`nrow(E2 %>% filter(targetSide!="Both")) / nrow(E2)`

@@

Fit mixture model (if fitting not previously done and cached). 
```{r, echo=FALSE}
#devtools::install_github('alexholcombe/mixRSVP',build_vignettes=TRUE)
library(mixRSVP)

@@

estimates<- E2  %>%  filter( !is.nan(targetSP) ) %>% filter(subject>"AF") %>%
    group_by_(.dots = condtnVariableNames) %>%  #.dots needed when you have a variable containing multiple factor names
    do(  analyzeOneConditionDF(.,numItemsInStream,parameterBounds(),nReplicates=5) )

@@

Save the param estimates to a file.
```{r SaveParamEstimates, echo=FALSE}

resultsPath<- file.path("Results")

write.csv(estimates, file = file.path(resultsPath, "backwards2E2_paramEstimates.csv"))
#saveRDS(estimates, file = file.path(resultsPath, "Results/backwards2E1_paramEstimates.rda"), compress="bzip2")

### 2018-08-17 E2/analysis/validateE2data.Rmd
about to build renaming columns into import

---
title: "importE2data"
author: "Alex Holcombe"
date: "2/27/2018"
output: html_document
---

@@

>>>>

---
title: "validateE2data"
author: "Alex Holcombe"
date: "2/27/2018"
output: html_document
---
Optional validation (don't need to run this), loads raw data on its own and validates a few things

@@

Sanity-check some data by graphing.

Investigate whether pathological identicalness of inverted/canonical happens, that happened in E1 . Seems it doesn't

```{r}
dg<- E2 %>% filter(subject < "AC")

library(ggplot2)
g=ggplot(dg, aes(x=SPE)) + facet_grid(subject+orientation~stream) #,  scales="free_y")
g<-g+geom_histogram(binwidth=1,color="grey90") + xlim(minSPE,maxSPE)
g<-g+ geom_text(x=12, y= 33, aes(label = subject)) #inset subject name/number. Unfortunately it overwrites itself a million times
show(g)
```
